Automatic Matching of Bullet Lands

### 2016-01-06 imaging-paper.Rnw
refer to extended hamby results

>>>>

\hh{Besides including results from known matches againts known non-matches, we can increase the number of comparisons in the Hamby study to include all possible land-to-land comparisons. This effectively doubles the number of data points available. Comparisons not previously included in fitting the random forest can also be used as an additional source for assessing error rates.  Results for this and a more detailed discussion can be found in supplement section~\ref{supp:extended}.}
